```{r init,message=F,warning=F,include=F}
rm(list = ls())
cat('\014')
source('src.R')
```

Hello! These functions use the `ngramr` package to query the Google Books Ngrams database. We'll use them to answer the question, "Which came first, the chicken or the egg?" After you've gone through the demo, feel free to change the `query` argument to ask your own "Which came first?" question.

# Querying Google Ngrams

```{r collect-data}
tts<-gbng2tts.f(
  query = 
    # ec('social,society') # box: inconclusive 4 year lag # fails
    # ec('society,sociology') # box: some support 3 year lag # inconclusive
    # ec('sociology,sociological') # box: right on top or possible 17 year lag (length of zero series?) # weak support (AIC)
    # ec('sociological,sociologist') # box: nothing/right on top # right on top of each other
    # ec('sociologist,sociology of') # box: fail # inconclusive order but strong 7 year lag
	,ys = 1850
	,ye = 2008
	,sm = 0
	,cfso=F
)

```

```{r inspect}
tts
```

# Visualize

```{r plot-data,include=T,eval=T}
grgr<-tts2grgr.f(
	gbng2tts=tts
	,mxlg = 20
)
grgr$plot
```

## Which Came First? Granger Causality

Adapted from the R-Bloggers post [Chicken or the Egg? Granger-Causality for the masses](https://www.r-bloggers.com/chicken-or-the-egg-granger-causality-for-the-masses/) by Cory Lesmeister.


